
\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
125 South Webster Street & {\it Voice:}  (608) 301-5067 \\            
P.O. Box 7841 & {\it Fax:}    (608) 263-6448  \\         
Wisconsin Department of Public Instruction & {\it E-mail:}  jknowles@gmail.com\\       
Madison, WI  53707-7841 & {\it www:} \url{www.jaredknowles.com} \\     
\end{tabular}


\section{\sc Research Interests}
Education governance, federalism, public policy, the bureaucracy, dropout early warning systems, Bayesian statistics, applied statistical modeling, analysis of administrative records, data visualization

\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 
WCER Interdisciplinary Training Program IES Pre-Doctoral Fellow at WCER, 2009-2015

\section{\sc Policy Experience}
{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Research Analyst} \hfill {\bf January 2013 - Present}\\
Support agency policy development and advancement of the State Superintendent's agenda through analysis of statewide longitudinal student data and other available data to support evidenced based policy making. 
\begin{list2}
\item Develop, pilot, and deploy early warning systems for educational outcomes using large-scale statewide datasets. 
\item Support evidenced based policymaking with quick turnaround analyses of statewide datasets. 
\item Grow agency-wide data literacy and skillsets by conducting in-house training in data use and statistical computing.
\end{list2}

\vspace{-.3cm}
{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013}\\
Conduct policy research using administrative records on a tight timeline to support key decision making efforts. 
\begin{list2}
\item Apply classification models to state administrative records to identify policy needs for reading and math statewide.
\item Support agency strategic goal setting with projections of future education performance.
\item Building partnerships with external researchers to improve quality and timeliness of research for supporting agency decisions.
\item Serve as Pupil Data Policy Advisor and the Human Subject Protections Administrator to ensure compliance with state and federal laws for pupil privacy and ethical research.
\end{list2}

\vspace{-.3cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
\begin{list2}
\item Statistical analysis of state bilingual bicultural categorical aid program to inform the budget process.
\item Developed software for geo-referencing administrative records to generate maps of administrative data.
\item Analyze teacher licensure data for patterns in distribution of teachers across the state.
\end{list2}

{\bf Office of the Governor}, Madison, Wisconsin USA

{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Present comparisons of national education data, create data visualizations of state education performance data, and conduct analysis of Wisconsin RTTT application. 
\begin{list2}
\item Coordinated and presented analysis of applications by other states.
\item Worked with the state education agency to develop achievement targets grounded in data.
\end{list2}

\section{\sc Academic Experience}
{\bf University of Wisconsin-Madison}, Madison, Wisconsin USA

\vspace{-.1cm}
{\em Teaching Assistant} \hfill {\bf August 2008 - June, 2009}\\
Lead section and exam review sessions, graded homework and exams, provided academic support to undergraduate students.
\vspace*{.05in}  
\begin{list2}
\item POLS 466: Campaign Finance, Professor Ken Mayer
\item POLS 452: Criminal Law, Professor Donald Downs
\end{list2}


%\vspace{-.1cm}
{\em Research Assistant} \hfill {\bf February-May 2009}\\
Consultant for Arizona Clean Elections Commission. Collected and analyzed data on candidate campaign finance reports under direction from Professor Ken Mayer. 
\vspace*{.05in}  


{\bf Pacific University}, Forest Grove, Oregon USA

\vspace{-.3cm}
{\em Research Assistant} \hfill {\bf September 2007 - May 2008}\\
Reviewed literature and provided comprehensive summaries in support of Professor Jeff Seward's "Democracy and Inequality" project.

\vspace*{5mm}


\section{\sc Publications}

Knowles, Jared E. and Zach Mayer. (2015). caretEnsemble: A Framework for combining 
caret models into ensembles. R package version 1.0. \url{http://CRAN.R-project.org/package=caretEnsemble}

Knowles, Jared E. (2014). Of Needles and Haystacks: Building an Accurate Statewide Dropout Early Warning System in Wisconsin. figshare. \url{http://dx.doi.org/10.6084/m9.figshare.1142580}
[Forthcoming at the Journal of Education Data Mining]

Knowles, Jared E. and Douglas White (2013). \emph{The Wisconsin Dropout Early Warning System (DEWS) Action Guide for Educators.} Wisconsin Department of Public Instruction. Madison, WI. \url{http://wise.dpi.wi.gov/files/wise/pdf/wi-dews-actionguide2013.pdf}

\section{\sc Selected Manuscripts in Preparation}

Knowles, Jared and Deven Carlson. ``The Effect of English Proficiency Classification on Future Outcomes: Evidence from a Statewide Discontinuity.'' [Revise and Resubmit at the Journal of Policy Analysis and Management]

Knowles, Jared, Andy Reschovsky, and Lindsay Amiel. ``The Political Economy of Voter Support for School Property Taxation'' 

Knowles, Jared and Deven Carlson. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bilcultural Education Programs on English Language Proficiency and Reading and Mathematics Achievement.'' [Under review at American Education Research Journal]

\vspace*{5mm}

\section{\sc Conference Presentations}

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' 107$^{th}$ Annual Conference on Taxation of the National Tax Association, Santa Fe, NM. November 13$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``An Early Warning System for You: Wisconsin’s Open Source Predictive Analytic Approach.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $31^{st}$, 2014.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' Conference of the Association of Educational Finance and Policy, San Antonio, TX. March 15$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``Building and Deploying an Early Warning System: Lessons Learned from a Large Scale Pilot.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $17^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' Conference of the Association of Educational Finance and Policy, New Orleans, LA. March 16$^{th}$, 2013. 

\textbf{Knowles, Jared} and Doug White. ``Wisconsin's Dropout Early Warning System.'' Wisconsin School Counselor Association Annual Conference, Madison, WI. February, $20^{th}$, 2013. 

\textbf{Knowles, Jared}. ``Data Analysis Technical Assistance (DATA) User Group Meeting.'' \emph{Lead Facilitator}. $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Developing and Deploying a Statewide Early Warning System With R and State Longitudinal Data System (SLDS) Data.'' $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' 105$^{th}$ Annual Conference of the National Tax Association, Providence, RI. November 16$^{th}$, 2012. 

\textbf{Knowles, Jared}. ``Using R and Longitudinal Data System Records to Answer Policy Questions.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $11^{th}$, 2012.

\textbf{Knowles, Jared}. ``Using R for Policy Research in a State Education Agency: Lightning Talk'' $8^{th}$ International useR! Conference 2012, Nashville, TN. June 13$^{th}$ 2012.

\textbf{Knowles, Jared}. ``Policy Relevant Visualization and Analysis of Longitudinal Data Systems Data with Open Source Tools.'' $25^{th}$ Annual Management and Information Systems (MIS) Conference, San Diego, CA. January 20$^{th}$ 2012.

\section{\sc Professional Activities and Service}

Chair, State Superintendent's Wisconsin Education Research Advisory Council (WERAC), elected March $27^{th}$, 2012

Harvard University Strategic Data Project Cohort 5 Faculty Advisor

Wisconsin SEA Representative to the National Forum on Education Statistics, 2011 -- Present

Wisconsin Department of Public Instruction R User Group \emph{organizer}

Data Analysis Technical Assistance - Community of Practice in Education (DATA-COPE). \emph{founder, organizer} 

\end{resume}
\end{document}


