% CV

\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[normalem]{ulem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
Civilytics Consulting LLC & {\it Voice:}  (617) 393-0263 \\            
28 Rangeley Road & {\it www:} \url{www.civilytics.com} \\           
Watertown, MA 02472 & {\it E-mail:}  jared@civilytics.com\\       
 & {\it Twitter:} @jknowles      \\   
\end{tabular}


\section{\sc Research Interests}
Education governance, federalism, public policy, the bureaucracy, policing, 
public budgets, analysis of administrative records, data visualization

\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 

\href{https://www.lafollette.wisc.edu/news/2015-gladfelter-winners-announced}{Lloyd D. Gladfelter Award for Government Innovation} from the La Follette School of Public Affairs at UW-Madison, 2015

\vspace*{-2.5mm}

Interdisciplinary Training Program Fellowship at WCER, 2009-2015
% \vspace*{-2.5mm}
% Pacific University: graduated Summa cum laude, Outstanding Senior in the Social Sciences

\vspace*{-2.5mm}

German Academic Exchange Service (DAAD) Undergraduate Fellow, 2006-2007
% \vspace*{-2.5mm}
% Year of Study in Munich, Lewis and Clark College, 2006-2007



\section{\sc Publications}

Knowles, Jared. E. (2020). ``How to Take Back the Budget.'' \emph{Community Resource 
Hub for Safety \& Accountability.} \href{https://communityresourcehub.org/resources/how-to-take-back-the-budget/}{Available online.}

Knowles, Jared. E. (2020). ``Policing the American University.'' \emph{Civilytics 
Data Report} \#1. \href{https://www.civilytics.com/publication/cpd-report/}{Available online.}

Geller, Wendy, Dorothyjean Cratty, and Jared Knowles. (2019). \uline{Education Data Done Right: Lessons from the Trenches of Applied Data Science.} \emph{LeanPub.} 
\href{https://www.eddatadoneright.com}{Available online.}

Knowles, Jared E. and William Clune. (2016). ``Delivery of State-provided Predictive
Analytics to Schools: Wisconsin’s DEWS and the Proposed EWIMS Dashboard.'' 
\emph{WCER Working Paper.} No. 2016-3, July 2016. \href{https://wcer-web.ad.education.wisc.edu/docs/working-papers/Working_Paper_No_2016_03.pdf}{Available online.}

Knowles, Jared and Deven Carlson. (2016). ``The Effect of English Proficiency Classification on Future Outcomes: 
Evidence from a Statewide Discontinuity.'' \emph{Journal of Policy Analysis and Management.}
35:3, 559-586. 

% Knowles, Jared E. (2015). ``School Boards and the Democratic Promise,'' (PhD diss., University of 
% Wisconsin - Madison, 2015).

Knowles, Jared E. (2015). ``Of Needles and Haystacks: Building an Accurate Statewide 
Dropout Early Warning System in Wisconsin.'' \emph{Journal of Educational Data 
Mining.} 7:3, 18-67. 
\href{https://www.educationaldatamining.org/JEDM/index.php/JEDM/article/view/JEDM082}{Available online.}

Knowles, Jared E. (2015). eeptools: Convenience Functions for Education Data. R package
  version 0.9. \url{https://CRAN.R-project.org/package=eeptools}

Knowles, Jared E. and Carl Frederick. (2015). merTools: Tools for Analyzing Mixed 
Effect Regression Models. R package version 0.9. 
\url{https://CRAN.R-project.org/package=merTools}

% Knowles, Jared E. and Zach Mayer. (2015). caretEnsemble: Ensembles of Caret Models. 
% R package version 1.0. \url{https://CRAN.R-project.org/package=caretEnsemble}
% 
% Knowles, Jared E. (2014). EWStools. figshare. \url{https://dx.doi.org/10.6084/m9.figshare.1142590}

% Knowles, Jared E. (2014). Knowles R Bootcamp. figshare. 
% \url{https://dx.doi.org/10.6084/m9.figshare.1150042}

Knowles, Jared E. and Douglas White (2013). \emph{The Wisconsin Dropout Early 
Warning System (DEWS) Action Guide for Educators.} Wisconsin Department of Public 
Instruction. Madison, WI. \href{https://dpi.wi.gov/dews}{Available online.}

% \section{\sc Manuscripts in Preparation}

% Knowles, Jared, Dominique Bradley, and Sara Dahill-Brown. ``Politics, Capacity, and Distributional Equity in the Administration of Competitive Grants.''

% 
% Knowles, Jared. ``Bringing Place Back In: Applying Spatial Analysis Techniques to Investigations of Political Phenomena.'' Submitted for a preliminary examination in June of 2011. UW-Madison Political Science Department. 
% 
% Knowles, Jared. ``Analyzing Implementation and Treatment Fidelity in a Large Randomized Control Trial through Multi-level Modeling.''

% \vspace*{5mm}

\vspace*{1mm}
\noindent\hfil\rule{0.7\textwidth}{.4pt}\hfil
\vspace*{1mm}

\section{\sc Grant Awards}

% (ED-GRANTS-031215-002)
Wisconsin Department of Public Instruction. 2015. Bringing Evidence Based 
Practices to Practitioners in Wisconsin. A proposal to the Institute of Education 
Sciences Statewide Longitudinal Data System Data Use Competition.  
[funded \$5.25 million over 4 years, project director]

% (HHS-2012-ACF-ACYF-CO-0270)
Wisconsin Department of Children and Families. 2012. Improving Outcomes for Children in Out of Home Care through Coordination. A proposal to the Administration of Children, Youth and Families 
 Child Welfare-Education System Collaboration to Increase Educational Stability Competition. [funded \$500,000 over 2 years]

Knowles, Jared. 2013. Dissertation Development Grant for Compilation of School Board Election Records Database. University of Wisconsin - Madison Summer Initiative Funds. [funded]

Knowles, Jared. 2012. Dissertation Development Grant for Collection of School Board Election Records. University of Wisconsin - Madison Summer Initiative Funds. [funded]

\vspace*{1mm}
\noindent\hfil\rule{0.7\textwidth}{.4pt}\hfil
\vspace*{1mm}


\section{\sc Policy Experience}
{\bf Civilytics Consulting LLC}, Watertown, Massachusetts USA


{\em President} \hfill {\bf August 2016 - Present}\\
Provide statistical analysis, policy recommendations, and training to government, 
journalists, non-profits, and the general public. 
\begin{list2}
\item Develop public reports on police funding, arrest behavior, and the campus 
policing sector to inform the public and policymakers using available data.
\item Develop analytic software to inform strategic planning for K-12 and higher 
education policymakers. 
\item Train hundreds of education data analysts in statistical methods, programming, 
and policy evaluation.
\item Train community organizations, journalists, and city officials on budget 
analysis with an emphasis on policing and corrections budgets. 
\end{list2}

\vspace{-.1cm}
{\bf Department of Public Instruction}, Madison, Wisconsin USA

{\em Research Analyst} \hfill {\bf January 2013 - June 2016}\\
Support agency policy development and advancement of the State Superintendent's agenda through analysis of statewide longitudinal student data and other available data to support evidenced based policy making. 
\begin{list2}
\item Develop, pilot, and deploy early warning systems for educational outcomes using large-scale statewide datasets. 
\item Support evidenced based policymaking and budget development with quick turnaround analyses of statewide datasets. 
\item Grow agency-wide data literacy and skillsets by conducting in-house training in data use and statistical computing.
\end{list2}

\vspace{-.3cm}
{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013}\\
Conduct policy research using administrative records on a tight timeline to support key decision making efforts. Also support development of agency research policy through developing a research agenda, building partnerships with academic institutions, and developing guidelines about how to utilize research for decision support.
\begin{list2}
\item Apply classification models to state administrative records to identify policy needs for reading and math statewide.
\item Support agency strategic goal setting with projections of future education performance.
\item Policy analysis of categorical aid programs using student-level administrative records.
\item Building partnerships with external researchers to improve quality and timeliness of research for supporting agency decisions.
%\item Chair, State Superintendent's Wisconsin Education Research Advisory Council (WERAC).
\item Serve as Pupil Data Policy Advisor and the Human Subject Protections Administrator to ensure compliance with state and federal laws for pupil privacy and ethical research.
\end{list2}

\vspace{-.3cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
Developed R code to analyze and visualize administrative record datasets, especially longitudinal student data on state accountability assessments. 
\begin{list2}
\item Statistical analysis of state bilingual bicultural categorical aid program to inform the budget process.
\item Developed software for geo-referencing administrative records to generate maps of administrative data.
\item Analyze teacher licensure data for patterns in distribution of teachers across the state.
\item Conducted several smaller policy analyses using statewide administrative records under a tight deadline during budget process.
\end{list2}

{\bf Office of the Governor}, Madison, Wisconsin USA

{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Present comparisons of national education data, create data visualizations of state education performance data, and conduct analysis of Wisconsin RTTT application. 
\begin{list2}
\item Coordinated and presented analysis of applications by other states.
\item Worked with the state education agency to develop achievement targets grounded in data.
\end{list2}

% \section{\sc Academic Experience}
% {\bf University of Wisconsin-Madison}, Madison, Wisconsin USA
% 
% \vspace{-.1cm}
% {\em Teaching Assistant} \hfill {\bf August 2008 - June, 2009}\\
% Lead section and exam review sessions, graded homework and exams, provided academic support to undergraduate students.
% \vspace*{.05in}  
% \begin{list2}
% \item POLS 466: Campaign Finance, Professor Ken Mayer
% \item POLS 452: Criminal Law, Professor Donald Downs
% \end{list2}
% 
% 
% %\vspace{-.1cm}
% {\em Research Assistant} \hfill {\bf February-May 2009}\\
% Consultant for Arizona Clean Elections Commission. Collected and analyzed data on candidate campaign finance reports under direction from Professor Ken Mayer. 
% \vspace*{.05in}  
% 
% 
% {\bf Pacific University}, Forest Grove, Oregon USA
% 
% \vspace{-.3cm}
% {\em Research Assistant} \hfill {\bf September 2007 - May 2008}\\
% Reviewed literature and provided comprehensive summaries in support of Professor Jeff Seward's "Democracy and Inequality" project.

\vspace*{1mm}
\noindent\hfil\rule{0.7\textwidth}{.4pt}\hfil
\vspace*{1mm}

\section{\sc Professional Activities and Service}
% 
\begin{list2}
\item Urban Institute Education Data Portal Advisory Board member, 2020-2021
\item Institute for Education Sciences Peer Review Panel Member, 2019
\item Faculty Advisor, Strategic Data Project, Center for Education Policy Research (CEPR) at Harvard University, 2012 -- present
\item National Forum on Education Statistics at the Institute for Education Sciences, \emph{state agency representative for Wisconsin}, 2011 -- 2016
\item Wisconsin Department of Public Instruction R User Group \emph{founder, organizer}, 
2012 -- 2016 
\item Data Analysis Technical Assistance-Community of Practice in Education 
(DATA-COPE) \emph{founder, organizer}, 2014 -- 2018
\item State Superintendent's Wisconsin Education Research Advisory Council (WERAC), 
\emph{chair, organizer}, 2012 -- 2016
\end{list2}

\vspace*{1mm}
\noindent\hfil\rule{0.7\textwidth}{.4pt}\hfil
\vspace*{1mm}


\section{\sc Invited Presentations}

Knowles, Jared. ``City and County Budget Deep Dive Training.'' Community Resource 
Hub for Safety \& Accountability. July through September 2020. Online. 

Knowles, Jared. ``Using Data to Inform Police Advocacy.'' Borealis Communities 
Transforming Policing Fund Grantees. February $20^{th}$ 2020. Online. 

Knowles, Jared and Wendy Geller. ``Doing Education Data Right.'' Winter 2020: 
Accountability Systems and Reporting Collaborative Meeting. Council of Chief 
State School Officers. February $19^{th}$ 2020. New Orleans, LA.

Knowles, Jared. ``Applying Predictive Analytics in Education Ethically.'' Summer 
Institute in Learning Analytics (SILA) 2019. The Center for Education Policy 
Research at Harvard University. July $17^{th}$ 2019. Cambridge, MA.

Knowles, Jared. ``Open Analytics.'' Colloquium 2018: Re-imagining Asessment 
and Accountability in an Open World. Center for Assessment. May $23^{rd}$ - $24^{th}$ 2018. 
Ketchum, ID. 

Knowles, Jared and Jason Becker. ``Making the Argument: Data Visualization and 
Persuasion.'' Strategic Data Project 2015 Convening. May $18^{th}$ - $19^{th}$ 2015. 

Knowles, Jared. ``An Education Information Portal for Child Welfare.'' Presentation to the Wisconsin Youth Services Conference. Wisconsin Dells, WI. April 22\textsuperscript{nd} 2015.

Knowles, Jared. ``Using Administrative Data to Conduct Rigorous Evaluations: Promises and Challenges.'' Guest Lecture to UW-Madison La Follette School of Public Affairs, Madison, WI. October $20^{th}$ 2014.

Knowles, Jared. ``Strategy, Leadership, and Narratives: Data Viz for Policy Change.'' Invitational Summit on Educational Data Visualization, Austin, TX. May $6^{th}$ 2014. 

Knowles, Jared. ``Data Visualization for Education Data.'' Strategic Data Project Institute for Leadership in Analytics. Strategic Data Project, Cambridge, MA. February $14^{th}$ 2014. 

Knowles, Jared. ``Statistical Learning and Applied Modeling in Education: Examples 
and Concerns.'' Guest Lecture at the Interdisciplinary Training Seminar in Education Sciences, Wisconsin Center for Education Research, Madison, WI. January $31^{st}$ 2014.

Knowles, Jared and Kurt Kiefer. ``Building and Deploying a Predictive Risk Model Statewide in Wisconsin: Lessons Learned.'' Invited talk with the 
Wisconsin Department of Children and Families Executive Leadership Workshop. Madison, WI. December $17^{th}$ 2014.

Knowles, Jared. ``Using Statistical Models to Help Policymakers Avoid Mistakes.'' Guest Lecture to UW-Madison La Follette School of Public Affairs, Madison, WI. October $22^{nd}$ 2013.

Knowles, Jared. ``Data Visualization for Education Data.'' Strategic Data Project Winter Fellows Workshop. Strategic Data Project, Denver, CO. January $17^{th}$ 2013. 

Knowles, Jared. ``Strategies and Structures for Improving Data Use -- An SEA Perspective.'' Summer Institute for Leadership in Analytics--The Strategic Data Project. Harvard University, Boston, MA. August $5^{th}$ 2012. 

%Knowles, Jared. Discussant.  \emph{The Problem of Men: The University Gender Gap by Lesley Lavery and John Witte.} Issues for Universities in the $21^{st}$ Century Conference. Madison, WI. June $9^{th}$ 2012. 

Knowles, Jared. ``Math Achievement in Wisconsin--Where Are We Today?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. May $29^{th}$. 

% Knowles, Jared. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bicultural Education Programs on English Language Proficiency, Reading, and Mathematics Achievement.`` The 2012 Wisconsin English Language Learner Stakeholder Conference. Madison, WI. May $23^{rd}$ 2012. 

% Knowles, Jared. ``Background Data for Setting Educational Goals.'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. January $23^{rd}$ 2012. 

Knowles, Jared. ``Using Data to Identify Priorities in an Accountability System.'' Wisconsin School and District Accountability Design Team. September 22$^{nd}$, 2011.

% Knowles, Jared. ``Background on Wisconsin K-12 Education from Administrative Data.'' Wisconsin Education Research Advisory Council Inaugural Meeting. Madison, WI. October 13$^{th}$ 2011.

% Knowles, Jared. ``How to Promote Change in Reading Achievement?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. August 22$^{nd}$ 2011.

Knowles, Jared. ``Reading Achievement in the National Context.'' Cabinet of the Department of Public Instruction--Wisconsin. June 29$^{th}$ 2011.

% Knowles Jared. ``Finding Balance Between Policy, Research, and Randomized Trials.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. April 29$^{th}$, 2011.
% 
% Knowles, Jared, Dominique Dust, and Sara Dahill-Brown. ``Winning, Losing, and Writing Race to the Top Grants: Bridging Research to Policy.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. February 11$^{th}$, 2011.

Knowles, Jared. ``An Evaluation of the Effectiveness of Bilingual and Bicultural Education Programs on English Proficiency.'' Department of Public Instruction--Wisconsin. October $23^{rd}$, 2010. 

\section{\sc Conference Presentations}

Levesque, Karen and \textbf{Jared Knowles}. ``Two Sides of the Same Coin: State 
Staff and Researcher Perspectives on State Longitudinal Data.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $8^{th}$, 2015.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' 107$^{th}$ Annual Conference on Taxation of the National Tax Association, Santa Fe, NM. November 13$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``An Early Warning System for You: Wisconsin’s Open Source Predictive Analytic Approach.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $31^{st}$, 2014.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' Conference of the Association of Educational Finance and Policy, San Antonio, TX. March 15$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``Building and Deploying an Early Warning System: Lessons Learned from a Large Scale Pilot.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $17^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' Conference of the Association of Educational Finance and Policy, New Orleans, LA. March 16$^{th}$, 2013. 

\textbf{Knowles, Jared} and Doug White. ``Wisconsin's Dropout Early Warning System.'' Wisconsin School Counselor Association Annual Conference, Madison, WI. February, $20^{th}$, 2013. 

\textbf{Knowles, Jared}. ``Data Analysis Technical Assistance (DATA) User Group Meeting.'' \emph{Lead Facilitator}. $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Developing and Deploying a Statewide Early Warning System With R and State Longitudinal Data System (SLDS) Data.'' $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' 105$^{th}$ Annual Conference of the National Tax Association, Providence, RI. November 16$^{th}$, 2012. 

\textbf{Knowles, Jared}. ``Using R and Longitudinal Data System Records to Answer Policy Questions.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $11^{th}$, 2012.

\textbf{Knowles, Jared}. ``Using R for Policy Research in a State Education Agency: Lightning Talk'' $8^{th}$ International useR! Conference 2012, Nashville, TN. June 13$^{th}$ 2012.

\textbf{Knowles, Jared}. ``Policy Relevant Visualization and Analysis of Longitudinal Data Systems Data with Open Source Tools.'' $25^{th}$ Annual Management and Information Systems (MIS) Conference, San Diego, CA. January 20$^{th}$ 2012.

% \textbf{Knowles, Jared} and Deven Carlson. 2011. ``Is Bilingual Better? Using Statewide Longitudinal Data to Examine the Effect of Bilingual-Bicultural Programs on English Proficiency and Reading and Mathematics Achievement''. Association of Public Policy Analysis and Management 2011 Fall Research Conference, Poster Session, Washington, D.C., November 2011.

% AERA Annual Meeting, American Educational Research Association, \emph{attendee}, April $28^{th}$ to May $2^{nd}$ 2013, San Francisco, CA.

% Winter 2013 National Forum on Education Statistics Meeting. \emph{Wisconsin SEA representative}, February $10^{th}$ to the $13^{th}$, Washington D.C.
% 
% Introduction to Structural Equation Modeling. \emph{participant}, January $7^{th}$ -- $9^{th}$, Center for Integrated Latent Variable Research (CLIVR), College Park, MD.



% $2^{nd}$ Wisconsin Department of Public Instruction R Bootcamp. \emph{developer and instructor}, December $3^{rd}$ -- $5^{th}$, Madison, WI
% 
% $1^{st}$ Wisconsin Department of Public Instruction R Bootcamp. \emph{developer and instructor}, August $2^{nd}$ \& $3^{rd}$, Madison, WI

% Summer 2012 National Forum on Education Statistics Meeting, \emph{Wisconsin SEA representative}, July $9^{th}$ to the $11^{th}$, Washington D.C.

% Achieving Success at Scale Research on Scaling Up Effective High Schools Conference, The National Center on Scaling Up Effective Schools, June $10^{th}$ -- $12^{th}$ 2012, Nashville, Tennessee

% AERA Annual Meeting, American Educational Research Association, \emph{attendee}, April $11^{th}$ to April $16^{th}$ 2012, Vancouver, Canada.



% Winter 2012 National Forum on Education Statistics Meeting, \emph{Wisconsin SEA representative}, February $12^{th}$ to the $15^{th}$, San Diego, California

% State Longitudinal Data Systems P-20W Best Practices Conference, Department of Education, \emph{Wisconsin SEA representative}, November $15^{th}$ -- $16^{th}$, Washington D.C.

% Association of Public Policy Analysis and Management 2011 Fall Research Conference, APPAM, \emph{attendee}, November $7^{th}$ to November $9^{th}$ 2011, Washington D.C.

% Inaugural Meeting, State Superintendent's Wisconsin Education Research Advisory Council (WERAC), \emph{organizer}, October $16^{th}$ 2011, Madison, Wisconsin

%State Superintendent's Wisconsin Education Research Advisory Council (WERAC), \emph{member}, September 2011 -- present. Madison, Wisconsin

%STATS-DC LDS Data Conference, Department of Education, \emph{Wisconsin SEA representative}, July $27^{th}$ -- July $29^{th}$ 2011, Washington D.C. 

% AERA Annual Meeting, American Educational Research Association, \emph{attendee}, April $8^{th}$ to April $12^{th}$ 2011, New Orleans, LA.

%IES Research Conference, National Center for Education Statistics, \emph{attendee}, June $28^{th}$ to June $30^{th}$ 2010, Washington D.C. 

%CALDER Conference, Urban League, \emph{attendee}, August $12^{th}$ 2009, Washington D.C. 

% \section{\sc Consulting}
% 
% I provide a wide variety of statistical, policy, and statistical computing 
% consulting services to public and private sector clients at the national, state, 
% and local levels of government. 


\section{\sc Skills} 
\begin{list2}
\item Statistical Packages:  R, Stan, Stata
\item Languages:  R, Python, SQL, \LaTeX
\item R Packages: Creator \textbf{merTools}, \textbf{eeptools}, deep experience with caret, ggplot2, data.table, knitr, lme4, and more
\item Operating Systems:  Ubuntu, Windows
\item For more information visit GitHub: \url{https://www.github.com/jknowles}\\
\end{list2}

\section{\sc Statistical Training}
\begin{list2}
\item Multivariate regression
\item Mixed effect modeling, including hierarchical linear modeling
\item Applied predictive modeling and machine learning
\item Unsupervised learning and cluster analysis
\item Generalized linear modeling
\item Structural equation modeling
\item Bayesian analysis
\end{list2}

% \vspace{-2mm}
% \section{\sc Languages}
% 
% \begin{list2}
% \item English--native
% \item German--familiar
% \end{list2}

Last updated: 10/26/2020

\end{resume}
\end{document}
