% CV

\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[normalem]{ulem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
Civilytics Consulting LLC & {\it Voice:}  (617) 393-1939 \\            
14 Commonwealth Road & {\it www:} \url{www.jaredknowles.com} \\           
Watertown, MA 02472 & {\it E-mail:}  jknowles@gmail.com\\       
 & {\it Twitter:} @jknowles      \\   
\end{tabular}


\section{\sc Research Interests}
Democratic accountability, government performance analytics, applied statistical 
modeling, politics of evidence, criminal justice, education policy


\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 

\href{https://www.lafollette.wisc.edu/news/2015-gladfelter-winners-announced}{Lloyd D. Gladfelter Award for Government Innovation} from the La Follette School of Public Affairs at UW-Madison, 2015

\vspace*{-2.5mm}

Institute for Education Sciences Predoctoral Fellowship, Interdisciplinary Training Program (ITP) at Wisconsin Center for Education Research, 2009-2015

\section{\sc Work \\ Experience}
{\bf Civilytics Consulting LLC}, Watertown, Massachusetts USA

\vspace{-.3cm}
{\em President} \hfill {\bf September 2016 - Present}\\
Designing and implementing data analytics that inform policymakers and enhance 
public understanding of the performance of government agencies.\\
\vspace{-2mm}
\begin{list2}
\item Develop an open source statistical computing curriculum for state and 
local government employees.
\item Advise government agencies on machine learning early warning system design. 
\item Develop a comprehensive database of US police department performance measures.
\end{list2}
\vspace{-.1cm}

{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Senior Research Analyst} \hfill {\bf January 2013 - June 2016}\\
Supported advancement of the State Superintendent's agenda by producing quantitative 
analyses tailored for stakeholders, policymakers, and educators. \\
\vspace{-2mm}
\begin{list2}
\item Developed, piloted, and deployed early warning systems for educational outcomes 
used by hundreds of educators statewide. 
\item Guided evidenced-based policymaking with quick turnaround analyses of large administrative datasets. 
\item Grew state government employee data literacy and statistical computing skills by developing and 
leading dozens of regular training workshops.
\end{list2}

\vspace*{-.3cm}
{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013} \\
Conducted policy research using administrative records on a tight timeline to 
support key decisions by senior agency leadership. \\

\vspace*{-2mm}

\begin{list2}
\item Supported agency strategic goal setting with accurate projections of education performance.
\item Built partnerships with external researchers to improve quality and 
timeliness of research for supporting agency decisions.
\item Served as Pupil Data Policy Advisor and the Human Subject Protections 
Administrator to ensure compliance with state and federal laws for pupil privacy 
and ethical research.
\item Created statistical models to better target training and support to school districts.
\end{list2}

\vspace{-.3cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
Provided statistical programming support to the Office of Education Accountability.
\begin{list2}
\item Developed a quasi-experimental evaluation of the state bilingual bicultural 
categorical aid program to inform the budget process.
\item Developed software for geo-referencing administrative records to generate 
maps.
\item Trained agency analysts to use R to enhance reproducibility of agency analytics. 
\end{list2}
\vspace{-.1cm}

{\bf Office of the Governor}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Assisted in preparing Wisconsin's Race to the Top federal education funding 
application. 
\begin{list2}
\item Worked with the state education agency staff to develop achievement targets grounded in data.
\item Presented data visualization of comparative education data to senior policymakers.
\end{list2}


\section{\sc Publications}

Knowles, Jared E. and Carl Frederick. (2018). merTools: Tools for Analyzing Mixed 
Effect Regression Models. R package version 0.4.1. 
\url{https://CRAN.R-project.org/package=merTools}

Knowles, Jared E. (2018). eeptools: Convenience Functions for Education Data. 
R package version 1.2.0. \url{https://CRAN.R-project.org/package=eeptools}

Knowles, Jared E. and William Clune. (2016). ``Delivery of State-provided Predictive
Analytics to Schools: Wisconsin’s DEWS and the Proposed EWIMS Dashboard.'' 
\emph{WCER Working Paper.} No. 2016-3, July 2016. \href{http://wcer-web.ad.education.wisc.edu/docs/working-papers/Working_Paper_No_2016_03.pdf}{Available online.}

Knowles, Jared E. and Deven Carlson. (2016). ``The Effect of English Proficiency Classification on Future Outcomes: 
Evidence from a Statewide Discontinuity.'' \emph{Journal of Policy Analysis and Management.}
35:3, 559-586. 

Knowles, Jared E. (2015). ``Of Needles and Haystacks: Building an Accurate Statewide 
Dropout Early Warning System in Wisconsin.'' \emph{Journal of Educational Data 
Mining.} 7:3, 18-67. 
\href{http://www.educationaldatamining.org/JEDM/index.php/JEDM/article/view/JEDM082}{Available online.}

Knowles, Jared E. and Zach Mayer. (2015). caretEnsemble: A Framework for combining 
caret models into ensembles. R package version 1.0. \url{http://CRAN.R-project.org/package=caretEnsemble}

Knowles, Jared E. and Douglas White (2013). \emph{The Wisconsin Dropout Early Warning System (DEWS) Action Guide for Educators.} Wisconsin Department of Public Instruction. Madison, WI. \url{http://wise.dpi.wi.gov/files/wise/pdf/wi-dews-actionguide2013.pdf}

\section{\sc Manuscripts in Preparation}

Knowles, Jared E., Wendy Geller, and Dorothyjean Cratty. \uline{Data Analytics in 
Education: Not Another Fluffy Generic Book.} [Forthcoming: October 2018].

Knowles, Jared E. and Deven Carlson. ``Rethinking the Politics of Evidence Based 
Policy.'' 

Knowles, Jared E., Andy Reschovsky, and Lindsay Amiel. ``The Political Economy of 
Voter Support for School Property Taxation'' 


\vspace*{5mm}

\section{\sc Conference Presentations}

\textbf{Knowles, Jared}, Dahlin, Lauren, and Miriam Greenberg. ``OpenSDP: Making 
Education Data Analytics Open for All'' 
Strategic Data Project 2017 Convening, Boston, MA. May $17^{th}$ - $19^{th}$ 2017.

Levesque, Karen and \textbf{Jared Knowles}. ``Two Sides of the Same Coin: State 
Staff and Researcher Perspectives on State Longitudinal Data.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $8^{th}$, 2015.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' 107$^{th}$ Annual Conference on Taxation of the National Tax Association, Santa Fe, NM. November 13$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``An Early Warning System for You: Wisconsin’s Open Source Predictive Analytic Approach.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $31^{st}$, 2014.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' Conference of the Association of Educational Finance and Policy, San Antonio, TX. March 15$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``Building and Deploying an Early Warning System: Lessons Learned from a Large Scale Pilot.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $17^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' Conference of the Association of Educational Finance and Policy, New Orleans, LA. March 16$^{th}$, 2013. 

\textbf{Knowles, Jared} and Doug White. ``Wisconsin's Dropout Early Warning System.'' Wisconsin School Counselor Association Annual Conference, Madison, WI. February, $20^{th}$, 2013. 

\textbf{Knowles, Jared}. ``Data Analysis Technical Assistance (DATA) User Group Meeting.'' \emph{Lead Facilitator}. $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Developing and Deploying a Statewide Early Warning System With R and State Longitudinal Data System (SLDS) Data.'' $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' 105$^{th}$ Annual Conference of the National Tax Association, Providence, RI. November 16$^{th}$, 2012. 

\textbf{Knowles, Jared}. ``Using R and Longitudinal Data System Records to Answer Policy Questions.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $11^{th}$, 2012.

\textbf{Knowles, Jared}. ``Using R for Policy Research in a State Education Agency: Lightning Talk'' $8^{th}$ International useR! Conference 2012, Nashville, TN. June 13$^{th}$ 2012.

\textbf{Knowles, Jared}. ``Policy Relevant Visualization and Analysis of Longitudinal Data Systems Data with Open Source Tools.'' $25^{th}$ Annual Management and Information Systems (MIS) Conference, San Diego, CA. January 20$^{th}$ 2012.

\section{\sc Select Invited Presentations}

Knowles, Jared. ``An Education Information Portal for Child Welfare.'' Presentation to the Wisconsin Youth Services Conference. Wisconsin Dells, WI. April 22\textsuperscript{nd} 2015.

Knowles, Jared. ``Using Administrative Data to Conduct Rigorous Evaluations: Promises and Challenges.'' Guest Lecture to UW-Madison La Follette School of Public Affairs, Madison, WI. October $20^{th}$ 2014.

Knowles, Jared. ``Strategy, Leadership, and Narratives: Data Viz for Policy Change.'' Invitational Summit on Educational Data Visualization, Austin, TX. May $6^{th}$ 2014. 

Knowles, Jared. ``Statistical Learning and Applied Modeling in Education: Examples 
and Concerns.'' Guest Lecture at the Interdisciplinary Training Seminar in Education Sciences, Wisconsin Center for Education Research, Madison, WI. January $31^{st}$ 2014.

Knowles, Jared and Kurt Kiefer. ``Building and Deploying a Predictive Risk Model Statewide in Wisconsin: Lessons Learned.'' Invited talk with the 
Wisconsin Department of Children and Families Executive Leadership Workshop. Madison, WI. December $17^{th}$ 2014.

Knowles, Jared. ``Using Statistical Models to Help Policymakers Avoid Mistakes.'' Guest Lecture to UW-Madison La Follette School of Public Affairs, Madison, WI. October $22^{nd}$ 2013.

Knowles, Jared. ``Data Visualization for Education Data.'' Strategic Data Project Winter Fellows Workshop. Strategic Data Project, Denver, CO. January $17^{th}$ 2013. 

Knowles, Jared. ``Strategies and Structures for Improving Data Use -- An SEA Perspective.'' Summer Institute for Leadership in Analytics--The Strategic Data Project. Harvard University, Boston, MA. August $5^{th}$ 2012. 
Knowles, Jared. ``Math Achievement in Wisconsin--Where Are We Today?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. May $29^{th}$. 


Knowles, Jared. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bicultural Education Programs on English Language Proficiency, Reading, and Mathematics Achievement.`` The 2012 Wisconsin English Language Learner Stakeholder Conference. Madison, WI. May $23^{rd}$ 2012.

Knowles, Jared. ``Background Data for Setting Educational Goals.'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. January $23^{rd}$ 2012.

Knowles, Jared. ``Background on Wisconsin K-12 Education from Administrative Data.'' Wisconsin Education Research Advisory Council Inaugural Meeting. Madison, WI. October 13$^{th}$ 2011.

Knowles, Jared. ``Using Data to Identify Priorities in an Accountability System.'' Wisconsin School and District Accountability Design Team. September 22$^{nd}$, 2011.

Knowles, Jared. ``How to Promote Change in Reading Achievement?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. August 22$^{nd}$ 2011.

Knowles, Jared. ``Reading Achievement in the National Context.'' Cabinet of the Department of Public Instruction--Wisconsin. June 29$^{th}$ 2011.

Knowles Jared. ``Finding Balance Between Policy, Research, and Randomized Trials.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. April 29$^{th}$, 2011.

Knowles, Jared, Dominique Dust, and Sara Dahill-Brown. ``Winning, Losing, and Writing Race to the Top Grants: Bridging Research to Policy.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. February 11$^{th}$, 2011.

Knowles, Jared. ``An Evaluation of the Effectiveness of Bilingual and Bicultural Education Programs on English Proficiency.'' Department of Public Instruction--Wisconsin. October $23^{rd}$, 2010. 

\section{\sc Professional Activities and Service}

\begin{list2}
\item Harvard Strategic Data Project, \emph{faculty advisor, lead instructor}, 2013 -- present
\item National Forum on Education Statistics, \emph{state agency representative for Wisconsin}, 
2011 -- 2015
\item Wisconsin Department of Public Instruction R User Group \emph{founder, organizer}, 
2012 -- 2016 
\item Data Analysis Technical Assistance-Community of Practice in Education 
(DATA-COPE) \emph{founder, organizer}, 2014 -- 2018
\item State Superintendent's Wisconsin Education Research Advisory Council (WERAC), 
\emph{chair, organizer}, 2012 -- 2016
\end{list2}
 
\section{\sc Computing \\ Skills} 
\begin{list2}
\item Statistical Packages: R, Stata
\item Languages:  R, Stan, Python, SQL, \LaTeX
\item R Packages: merTools, eeptools, caret, 
ggplot2, tidyverse, rmarkdown, shiny, lavaan, lme4
\item For more details visit GitHub: \url{https://www.github.com/jknowles}\\
\end{list2}

\section{\sc Statistical Training}
\begin{list2}
\item Mixed effect modeling, including hierarchical linear modeling
\item Applied predictive modeling and machine learning
\item Unsupervised learning and cluster analysis
\item Structural equation modeling
\item Bayesian analyses
\end{list2}

\vspace{-2mm}
\section{\sc Languages}

\begin{list2}
\item English--native
\item German--familiar
\end{list2}


\end{resume}
\end{document}


