\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[normalem]{ulem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
Civilytics Consulting LLC & {\it Voice:}  (617) 393-1939 \\            
14 Commonwealth Road & {\it www:} \url{www.civilytics.com} \\           
Watertown, MA 02472 & {\it E-mail:}  jared@civilytics.com\\       
 & {\it Twitter:} @jknowles      \\   
\end{tabular}

\section{\sc Research Interests}
Democratic accountability, government performance analytics, applied statistical 
modeling, politics of evidence, criminal justice, education policy

\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
%\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
%\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 

\href{https://www.lafollette.wisc.edu/news/2015-gladfelter-winners-announced}{Lloyd D. Gladfelter Award for Government Innovation} from the La Follette School of Public Affairs at UW-Madison, 2015

\vspace*{-2.5mm}

Institute for Education Sciences Predoctoral Fellowship, Interdisciplinary Training Program (ITP) at Wisconsin Center for Education Research, 2009-2015

\vspace*{-2.5mm}
German Academic Exchange Service (DAAD) Undergraduate Fellow, 2006-2007

\section{\sc Work \\ Experience}
{\bf Civilytics Consulting LLC}, Watertown, Massachusetts USA

\vspace{-.3cm}
{\em President} \hfill {\bf September 2016 - Present}\\
Designing and implementing data analytics that inform policymakers and enhance 
public understanding of the performance of government agencies.\\
\vspace{-2mm}
\begin{list2}
\item Develop an open source statistical computing curriculum for state and 
local government employees in partnership with the Strategic Data Project at Harvard University.
\item Advise government agencies on machine learning early warning system design. 
\item Develop a comprehensive database of US police department performance measures.
\item Provide strategic advising on stakeholder engagement, ethical data analytic design, and development of streamlined data reporting tools tailored to audience needs.
\end{list2}
\vspace{-.1cm}

{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Senior Research Analyst} \hfill {\bf January 2013 - June 2016}\\
Supported advancement of the State Superintendent's agenda by producing quantitative 
analyses tailored for stakeholders, policymakers, and educators. \\

\vspace*{-.3cm}

{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013} \\
Conducted policy research using administrative records on a tight timeline to 
support key decisions by senior agency leadership. \\

\vspace{-.3cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
Provided statistical programming support to the Office of Education Accountability.

{\bf Office of the Governor}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Assisted in preparing Wisconsin's Race to the Top federal education funding 
application. 

% \begin{list2}
% \item Worked with the state education agency staff to develop achievement targets grounded in data.
% \item Presented data visualization of comparative education data to senior policymakers.
% \end{list2}

\section{\sc Select Publications}

Geller, Wendy, Dorothyjean Cratty, and Jared Knowles. (2019). \uline{Education Data Done Right: Lessons from the Trenches of Applied Data Science.} \emph{LeanPub.} \href{http://www.eddatadoneright.com}{Available online.}

Knowles, Jared E. (2020). ``Integrating Publicly Available External Data With an SLDS: Building 
Policy Relevance and Capacity.'' \emph{College & Career Readiness & Success Center.} 
SLDS Issue Brief. [Forthcoming, 2020]

Knowles, Jared E. and Carl Frederick. (2018). merTools: Tools for Analyzing Mixed 
Effect Regression Models. R package version 0.4.1. 
\url{https://CRAN.R-project.org/package=merTools}

Knowles, Jared E. and William Clune. (2016). ``Delivery of State-provided Predictive
Analytics to Schools: Wisconsin’s DEWS and the Proposed EWIMS Dashboard.'' 
\emph{WCER Working Paper.} No. 2016-3, July 2016. \href{http://wcer-web.ad.education.wisc.edu/docs/working-papers/Working_Paper_No_2016_03.pdf}{Available online.}

Knowles, Jared E. and Deven Carlson. (2016). ``The Effect of English Proficiency Classification 
on Future Outcomes: Evidence from a Statewide Discontinuity.'' \emph{Journal of Policy Analysis 
and Management.} 35:3, 559-586. 

Knowles, Jared E. (2015). ``School Boards and the Democratic Promise,'' (PhD diss., University of 
Wisconsin - Madison, 2015).

Knowles, Jared E. (2015). ``Of Needles and Haystacks: Building an Accurate Statewide 
Dropout Early Warning System in Wisconsin.'' \emph{Journal of Educational Data 
Mining.} 7:3, 18-67. 
\href{http://www.educationaldatamining.org/JEDM/index.php/JEDM/article/view/JEDM082}{Available online.}

Full publication list and details on all publications available online at 
\url{www.jaredknowles.com}


\vspace*{5mm}


\section{\sc Professional Activities and Service}
% 
\begin{list2}
\item Institute for Education Sciences Peer Review Panel Member, 2019
\item Faculty Advisor, Strategic Data Project, Center for Education Policy Research (CEPR) at Harvard University, 2012 -- 2019
\item National Forum on Education Statistics at the Institute for Education Sciences, \emph{state agency representative for Wisconsin}, 2011 -- 2016
\item Wisconsin Department of Public Instruction R User Group \emph{founder, organizer}, 
2012 -- 2016 
\item Data Analysis Technical Assistance-Community of Practice in Education 
(DATA-COPE) \emph{founder, organizer}, 2014 -- 2018
\item State Superintendent's Wisconsin Education Research Advisory Council (WERAC), 
\emph{chair, organizer}, 2012 -- 2016
\end{list2}


\section{\sc Statistical Training}
\begin{list2}
\item Mixed effect modeling, including hierarchical linear modeling
\item Applied predictive modeling, machine learning, deep learning with Keras
\item Unsupervised learning and cluster analysis
\item Structural equation modeling
\item Bayesian analyses
\item For more details visit GitHub: \url{https://www.github.com/jknowles}\\
\end{list2}

\vspace{-2mm}
\section{\sc Languages}

\begin{list2}
\item English--native
\item German--familiar
\end{list2}


\end{resume}
\end{document}


