% CV

\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
125 South Webster Street & {\it Voice:}  (608) 301-5067 \\            
P.O. Box 7841 & {\it Fax:}    (608) 263-6448  \\         
Wisconsin Department of Public Instruction & {\it E-mail:}  jknowles@gmail.com\\       
Madison, WI  53707-7841 & {\it www:} \url{www.jaredknowles.com} \\     
\end{tabular}


\section{\sc Research Interests}
Education governance, federalism, public policy, the bureaucracy, dropout early warning systems, Bayesian statistics, applied statistical modeling, analysis of administrative records, data visualization

\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 

Interdisciplinary Training Program Fellowship at WCER, 2009-2015

% \vspace*{-2.5mm}
% Pacific University: graduated Summa cum laude, Outstanding Senior in the Social Sciences

\vspace*{-2.5mm}
German Academic Exchange Service (DAAD) Undergraduate Fellow, 2006-2007

% \vspace*{-2.5mm}
% Year of Study in Munich, Lewis and Clark College, 2006-2007

\section{\sc Policy Experience}
{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.1cm}
{\em Research Analyst} \hfill {\bf January 2013 - Present}\\
Support agency policy development and advancement of the State Superintendent's agenda through analysis of statewide longitudinal student data and other available data to support evidenced based policy making. 
\begin{list2}
\item Develop, pilot, and deploy early warning systems for educational outcomes using large-scale statewide datasets. 
\item Support evidenced based policymaking with quick turnaround analyses of statewide datasets. 
\item Grow agency-wide data literacy and skillsets by conducting in-house training in data use and statistical computing.
\end{list2}

\vspace{-.1cm}
{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013}\\
Conduct policy research using administrative records on a tight timeline to support key decision making efforts. Also support development of agency research policy through developing a research agenda, building partnerships with academic institutions, and developing guidelines about how to utilize research for decision support.
\begin{list2}
\item Apply classification models to state administrative records to identify policy needs for reading and math statewide.
\item Support agency strategic goal setting with projections of future education performance.
\item Policy analysis of categorical aid programs using student-level administrative records.
\item Building partnerships with external researchers to improve quality and timeliness of research for supporting agency decisions.
\end{list2}

\vspace{-.1cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
Developed R code to analyze and visualize administrative record datasets, especially longitudinal student data on state accountability assessments. 
\begin{list2}
\item Statistical analysis of state bilingual bicultural categorical aid program to inform the budget process.
\item Developed software for geo-referencing administrative records to generate maps of administrative data.
\item Analyze teacher licensure data for patterns in distribution of teachers across the state.
\item Conducted several smaller policy analyses using statewide administrative records under a tight deadline during budget process.
\end{list2}

{\bf Office of the Governor}, Madison, Wisconsin USA

{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Present comparisons of national education data, create data visualizations of state education performance data, and conduct analysis of Wisconsin RTTT application. 
\begin{list2}
\item Coordinated and presented analysis of applications by other states.
\item Worked with the state education agency to develop achievement targets grounded in data.
\end{list2}

%\vspace*{5mm}

\vspace{-.1cm}
\section{\sc Publications}

Knowles, Jared E. (2013). eeptools: Convenience functions for education data. R package
  version 0.2. \url{http://CRAN.R-project.org/package=eeptools}

\vspace{-.1cm}
\section{\sc Manuscripts in Preparation}

Knowles, Jared, Dominique Bradley, and Sara Dahill-Brown. ``Politics, Capacity, and Distributional Equity in the Administration of Competitive Grants.''

Knowles, Jared. ``Needles, Haystacks, and Applied Modeling. Building an Early Warning System at 
Scale Using Statewide Longitudinal Data.'' (expected fall 2013). 

Knowles, Jared, Andy Reschovsky, and Lindsay Amiel. ``Understanding Property Tax Levies in an Era of Reduced State and Federal School Aid: The Case of Wisconsin.'' 

Knowles, Jared and Deven Carlson. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bilcultural Education Programs on English Language Proficiency and Reading and Mathematics Achievement.'' [Under review]

Knowles, Jared. ``Analyzing Implementation and Treatment Fidelity in a Large Randomized Control Trial.''

%\vspace*{5mm}

\section{\sc Conference Presentations}

\textbf{Knowles, Jared}. ``Building and Deploying an Early Warning System: Lessons Learned from a Large Scale Pilot.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $17^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' Conference of the Association of Educational Finance and Policy, New Orleans, LA. March 16$^{th}$, 2013. 

\textbf{Knowles, Jared} and Doug White. ``Wisconsin's Dropout Early Warning System.'' Wisconsin School Counselor Association Annual Conference, Madison, WI. February, $20^{th}$, 2013. 

\textbf{Knowles, Jared}. ``Data Analysis Technical Assistance (DATA) User Group Meeting.'' \emph{Lead Facilitator}. $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Developing and Deploying a Statewide Early Warning System With R and State Longitudinal Data System (SLDS) Data.'' $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' 105$^{th}$ Annual Conference of the National Tax Association, Providence, RI. November 16$^{th}$, 2012. 

\textbf{Knowles, Jared}. ``Using R and Longitudinal Data System Records to Answer Policy Questions.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $11^{th}$, 2012.

\textbf{Knowles, Jared}. ``Using R for Policy Research in a State Education Agency: Lightning Talk'' $8^{th}$ International useR! Conference 2012, Nashville, TN. June 13$^{th}$ 2012.

\textbf{Knowles, Jared}. ``Policy Relevant Visualization and Analysis of Longitudinal Data Systems Data with Open Source Tools.'' $25^{th}$ Annual Management and Information Systems (MIS) Conference, San Diego, CA. January 20$^{th}$ 2012.

\textbf{Knowles, Jared} and Deven Carlson. 2011. ``Is Bilingual Better? Using Statewide Longitudinal Data to Examine the Effect of Bilingual-Bicultural Programs on English Proficiency and Reading and Mathematics Achievement''. Association of Public Policy Analysis and Management 2011 Fall Research Conference, Poster Session, Washington, D.C., November 2011.

\section{\sc Invited Presentations}

Knowles, Jared. ``Data Visualization for Education Data'' Strategic Data Project Winter Fellows Workshop. Strategic Data Project, Denver, CO. January $17^{th}$ 2013. 

Knowles, Jared. ``Strategies and Structures for Improving Data Use -- An SEA Perspective.'' Summer Institute for Leadership in Analytics--The Strategic Data Project. Harvard University, Boston, MA. August $5^{th}$ 2012. 

%Knowles, Jared. Discussant.  \emph{The Problem of Men: The University Gender Gap by Lesley Lavery and John Witte.} Issues for Universities in the $21^{st}$ Century Conference. Madison, WI. June $9^{th}$ 2012. 

Knowles, Jared. ``Math Achievement in Wisconsin--Where Are We Today?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. May $29^{th}$. 

Knowles, Jared. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bicultural Education Programs on English Language Proficiency, Reading, and Mathematics Achievement.`` The 2012 Wisconsin English Language Learner Stakeholder Conference. Madison, WI. May $23^{rd}$ 2012. 

Knowles, Jared. ``Background Data for Setting Educational Goals.'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. January $23^{rd}$ 2012. 

Knowles, Jared. ``Using Data to Identify Priorities in an Accountability System.'' Wisconsin School and District Accountability Design Team. September 22$^{nd}$, 2011.

Knowles, Jared. ``How to Promote Change in Reading Achievement?'' Cabinet of the Department of Public Instruction--Wisconsin. Madison, WI. August 22$^{nd}$ 2011.

Knowles, Jared. ``Reading Achievement in the National Context.'' Cabinet of the Department of Public Instruction--Wisconsin. June 29$^{th}$ 2011.

Knowles Jared. ``Finding Balance Between Policy, Research, and Randomized Trials.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. April 29$^{th}$, 2011.

Knowles, Jared, Dominique Bradley, and Sara Dahill-Brown. ``Winning, Losing, and Writing Race to the Top Grants: Bridging Research to Policy.'' Wisconsin Center for Education Research--Interdisciplinary Training Program Seminar. February 11$^{th}$, 2011.

Knowles, Jared. ``An Evaluation of the Effectiveness of Bilingual and Bicultural Education Programs on English Proficiency.'' Department of Public Instruction--Wisconsin. October $23^{rd}$, 2010. 


\section{\sc Professional Activities and Service}

Wisconsin Department of Public Instruction R User Group. \emph{organizer}

Data Analysis Technical Assistance - Community of Practice in Education (DATA-COPE). \emph{organizer} 

Wisconsin Department of Public Instruction R Bootcamp. \emph{developer and instructor}, August $2^{nd}$ \& $3^{rd}$ and December $3^{rd}$ \& $5^{th}$ 2012, Madison, WI

State Superintendent's Wisconsin Education Research Advisory Council (WERAC). \emph{chair}, elected March $27^{th}$, 2012

Wisconsin SEA Representative to the National Forum on Education Statistics, November 2011--Present

Wisconsin Department of Public Instruction Pupil Data Policy Advisor, 2011-2013.

Wisconsin Department of Public Instruction Human Subject Protections Administrator, 2012-2013. 

\section{\sc Grant Awards}

Knowles, Jared. 2013. Dissertation Development Grant for Compilation of School Board Election Records Database. University of Wisconsin - Madison Summer Initiative Funds. [funded]

Wisconsin Department of Children and Families. 2012. Improving Outcomes for Children in Out of Home Care through Coordination. A proposal to the Administration of Children, Youth and Families 
 Child Welfare-Education System Collaboration to Increase Educational Stability Competition. (HHS-2012-ACF-ACYF-CO-0270) [funded from 09/30/2012 to 09/29/2014]

Knowles, Jared. 2012. Dissertation Development Grant for Collection of School Board Election Records. University of Wisconsin - Madison Summer Initiative Funds. [funded]

\section{\sc Skills} 
\begin{list2}
\item Statistical Packages:  R, JAGS, and Stata
\item Languages:  R, Processing, JavaScript
\item R Packages: Creator \textbf{eeptools}, deep experience with ggplot2, data.table, knitr, and more
\item Applications: QGIS, \LaTeX, Beamer, Processing, common Windows
  database, spreadsheet, and presentation software
\item Operating Systems:  Ubuntu, Ubuntu Server, SUSE Server, Windows
\item For more information visit GitHub: \url{http://www.github.com/jknowles}\\
\end{list2}

\vspace{-.5cm}
\section{\sc Statistical Training}
\begin{list2}
\item Multivariate regression
\item Mixed effect modeling, including hierarchical linear modeling
\item Predictive modeling and machine learning
\item Generalized linear modeling
\item Structural equation modeling
\item Bayesian analyses (including model averaging)
\item Machine learning algorithms including SVM, KNN, and neural networks 
\end{list2}

\vspace{-2mm}


\end{resume}
\end{document}


