% CV

\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
Civilytics Consulting LLC & {\it Voice:}  (617) 393-1939 \\            
14 Commonwealth Road & {\it www:} \url{www.jaredknowles.com} \\           
Watertown, MA 02472 & {\it E-mail:}  jknowles@gmail.com\\       
 & {\it Twitter:} @jknowles      \\   
\end{tabular}


\section{\sc Research Expertise}
Education governance, federalism, public policy, the bureaucracy, dropout early warning systems, Bayesian statistics, applied statistical modeling, analysis of administrative records, data visualization

\section{\sc Education}
\vspace*{-0.15mm}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA \\
\vspace*{-0.15mm}
Ph.D. in Political Science (May 2015) 

{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA \\
\vspace*{-0.15mm}
Master of Arts in Political Science (May 2009)

{\bf Pacific University}, Forest Grove, Oregon USA \\
\vspace*{-0.15mm}
Bachelor of Arts in Politics and Government (2008) \\
\vspace*{-0.15mm}
Bachelor of Arts in German Studies (2008) \\
\vspace*{-0.15mm}
Graduated \emph{Summa cum Laude} \\

% 
% 
% %{\em Department of Political Science} 
% \vspace*{-.1in}
% \begin{list1}
% \item[] Ph.D. Political Science, May, 2015
% \begin{list2}
% \vspace*{.05in}
% \item Subfields: American politics, political methodology
% \item Dissertation Title: \emph {School Boards and the Democratic Promise} 
% \item Advisor:  John Witte
% \end{list2}
% \vspace*{.05in}
% \item[] M.A., Political Science,  May 2009
% \end{list1}
% 
% {\bf Pacific University}, Forest Grove, Oregon USA\\
% %{\em Department of Politics and Government} 
% \vspace*{-.1in}
% \begin{list1}
% \item[] B.A., Politics and Government,  May, 2008
% \item[] B.A., German Studies, May, 2008
% \end{list1}

\vspace*{-2.0mm}
\section{\sc Honors, awards, and funding} 

% (ED-GRANTS-031215-002)
``Bringing Evidence Based Practices to Practitioners in Wisconsin.''
Institute of Education Sciences. [funded \$5.25 million over 4 years, project director]

\vspace*{-2.5mm}

% (HHS-2012-ACF-ACYF-CO-0270)
``Improving Outcomes for Children in Out of Home Care through Coordination.'' 
Administration of Children, Youth and Families. [funded \$500,000 over 2 years, education liaison]

\vspace*{-2.5mm}

\href{https://www.lafollette.wisc.edu/news/2015-gladfelter-winners-announced}{Lloyd D. Gladfelter Award for Government Innovation} from the La Follette School of Public Affairs at UW-Madison, 2015

\vspace*{-2.5mm}

Institue of Education Sciences Pre-Doctoral Interdisciplinary Training Program 
Fellowship, Wisconsin Center for Education Research, 2009-2015
% \vspace*{-2.5mm}
% Pacific University: graduated Summa cum laude, Outstanding Senior in the Social Sciences

% \vspace*{-2.5mm}

% German Academic Exchange Service (DAAD) Undergraduate Fellow, 2006-2007
% \vspace*{-2.5mm}
% Year of Study in Munich, Lewis and Clark College, 2006-2007
\vspace*{-2.5mm}
\section{\sc Relevant Publications}

Knowles, Jared E. and William Clune. (2016). ``Delivery of State-provided Predictive
Analytics to Schools: Wisconsin’s DEWS and the Proposed EWIMS Dashboard.'' 
\emph{WCER Working Paper.} No. 2016-3, July 2016. \href{http://wcer-web.ad.education.wisc.edu/docs/working-papers/Working_Paper_No_2016_03.pdf}{Available online.}

Knowles, Jared and Deven Carlson. (2016). ``The Effect of English Proficiency Classification on Future Outcomes: 
Evidence from a Statewide Discontinuity.'' \emph{Journal of Policy Analysis and Management.}
35:3, 559-586. 

Knowles, Jared E. (2015). ``School Boards and the Democratic Promise,'' (PhD diss., University of 
Wisconsin - Madison, 2015).

Knowles, Jared E. (2015). ``Of Needles and Haystacks: Building an Accurate Statewide 
Dropout Early Warning System in Wisconsin.'' \emph{Journal of Educational Data 
Mining.} 7:3, 18-67. 
\href{http://www.educationaldatamining.org/JEDM/index.php/JEDM/article/view/JEDM082}{Available online.}
% 
% Knowles, Jared E. (2015). eeptools: Convenience Functions for Education Data. R package
%   version 0.9. \url{http://CRAN.R-project.org/package=eeptools}
% 
% Knowles, Jared E. and Carl Frederick. (2015). merTools: Tools for Analyzing Mixed 
% Effect Regression Models. R package version 0.9. 
% \url{http://CRAN.R-project.org/package=merTools}
% 
% Knowles, Jared E. and Zach Mayer. (2015). caretEnsemble: Ensembles of Caret Models. 
% R package version 1.0. \url{http://CRAN.R-project.org/package=caretEnsemble}
% 
% Knowles, Jared E. (2014). EWStools. figshare. \url{http://dx.doi.org/10.6084/m9.figshare.1142590}
% % 
% Knowles, Jared E. (2014). Knowles R Bootcamp. figshare. 
% \url{http://dx.doi.org/10.6084/m9.figshare.1150042}

Knowles, Jared E. and Douglas White (2013). \emph{The Wisconsin Dropout Early 
Warning System (DEWS) Action Guide for Educators.} Wisconsin Department of Public 
Instruction. Madison, WI. \href{http://dpi.wi.gov/dews}{Available online.}

% \section{\sc Manuscripts in Preparation}

% Knowles, Jared, Dominique Bradley, and Sara Dahill-Brown. ``Politics, Capacity, and Distributional Equity in the Administration of Competitive Grants.''

% Knowles, Jared, Andy Reschovsky, and Lindsay Amiel. ``The Political Economy of Voter Support for School Property Taxation'' [Under review at Public Budgeting and Finance]
% \href{http://www.lafollette.wisc.edu/research-public-service/publications/the-political-economy-of-voter-support-for-school-property-taxation-v2}{Available online.}
% 
% Knowles, Jared, Andy Reschovsky, and Lindsay Amiel. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'' 
% 
% Knowles, Jared and Deven Carlson. ``Is Bilingual Better? Using Statewide Longitudinal Data to Analyze the Effect of Bilingual-Bilcultural Education Programs on English Language Proficiency and Reading and Mathematics Achievement.'' [Under review at American Education Research Journal]
% % 
% Knowles, Jared. ``Bringing Place Back In: Applying Spatial Analysis Techniques to Investigations of Political Phenomena.'' Submitted for a preliminary examination in June of 2011. UW-Madison Political Science Department. 
% 
% Knowles, Jared. ``Analyzing Implementation and Treatment Fidelity in a Large Randomized Control Trial through Multi-level Modeling.''

\vspace*{2.5mm}

\section{\sc Relevant Experience}
{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Research Analyst} \hfill {\bf January 2011 - June 2016}\\
Support agency policy development and advancement of the State Superintendent's agenda through analysis of statewide longitudinal student data and other available data to support evidenced based policy making. 
\begin{list2}
\item Develop, pilot, and deploy early warning systems for educational outcomes using large-scale statewide datasets. 
\item Grow agency-wide data literacy and skillsets by conducting in-house training in data use and statistical computing.
\item Develop absenteeism identification system and oversee research into impacts of 
absenteeism on short, medium, and long-range outcomes.
\end{list2}

\section{\sc Relevant Presentations}

Levesque, Karen and \textbf{Jared Knowles}. ``Two Sides of the Same Coin: State 
Staff and Researcher Perspectives on State Longitudinal Data.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $8^{th}$, 2015.

% Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' 107$^{th}$ Annual Conference on Taxation of the National Tax Association, Santa Fe, NM. November 13$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``An Early Warning System for You: Wisconsin’s Open Source Predictive Analytic Approach.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $31^{st}$, 2014.

% Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Political Economy of Voter Support for School Property Taxation'' Conference of the Association of Educational Finance and Policy, San Antonio, TX. March 15$^{th}$, 2014. 

\textbf{Knowles, Jared}. ``Building and Deploying an Early Warning System: Lessons Learned from a Large Scale Pilot.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $17^{th}$, 2013.

% Reschovsky, Andrew, Lindsay Amiel, and \textbf{Jared Knowles}. ``The Prospects of School Property Tax Revenue in the Wake of the 'Great Recession'.'' Conference of the Association of Educational Finance and Policy, New Orleans, LA. March 16$^{th}$, 2013. 
% 
\textbf{Knowles, Jared} and Doug White. ``Wisconsin's Dropout Early Warning System.'' Wisconsin School Counselor Association Annual Conference, Madison, WI. February, $20^{th}$, 2013. 

% \textbf{Knowles, Jared}. ``Data Analysis Technical Assistance (DATA) User Group Meeting.'' \emph{Lead Facilitator}. $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Developing and Deploying a Statewide Early Warning System With R and State Longitudinal Data System (SLDS) Data.'' $26^{th}$ Annual Management and Information Systems (MIS) Conference, Washington D.C. February $13^{th}$, 2013.

\textbf{Knowles, Jared}. ``Using R and Longitudinal Data System Records to Answer Policy Questions.'' STATS-DC National Center for Education Statistics Summer Data Conference, Washington D.C. July $11^{th}$, 2012.


\textbf{Knowles, Jared}. ``Policy Relevant Visualization and Analysis of Longitudinal Data Systems Data with Open Source Tools.'' $25^{th}$ Annual Management and Information Systems (MIS) Conference, San Diego, CA. January 20$^{th}$ 2012.

\textbf{Knowles, Jared}. ``Statistical Learning and Applied Modeling in Education: Examples 
and Concerns.'' Guest Lecture at the Interdisciplinary Training Seminar in Education Sciences, Wisconsin Center for Education Research, Madison, WI. January $31^{st}$ 2014.

% Knowles, Jared and Kurt Kiefer. ``Building and Deploying a Predictive Risk Model Statewide in Wisconsin: Lessons Learned.'' Invited talk with the 
% Wisconsin Department of Children and Families Executive Leadership Workshop. Madison, WI. December $17^{th}$ 2014.

\textbf{Knowles, Jared}. ``Using Statistical Models to Help Policymakers Avoid Mistakes.'' Guest Lecture to UW-Madison La Follette School of Public Affairs, Madison, WI. October $22^{nd}$ 2013.

\textbf{Knowles, Jared}. ``Data Visualization for Education Data.'' Strategic Data Project Winter Fellows Workshop. Strategic Data Project, Denver, CO. January $17^{th}$ 2013. 



\section{\sc Professional Activities and Service}
% 
\begin{list2}
\item Institute for Education Sciences Peer Review Panel Member, 2019
\item Faculty Advisor, Strategic Data Project, Center for Education Policy Research (CEPR) at Harvard University, 2012 -- 2019
\item National Forum on Education Statistics at the Institute for Education Sciences, \emph{state agency representative for Wisconsin}, 2011 -- 2016
\item Wisconsin Department of Public Instruction R User Group \emph{founder, organizer}, 
2012 -- 2016 
\item Data Analysis Technical Assistance-Community of Practice in Education 
(DATA-COPE) \emph{founder, organizer}, 2014 -- 2018
\item State Superintendent's Wisconsin Education Research Advisory Council (WERAC), 
\emph{chair, organizer}, 2012 -- 2016
\end{list2}

% \section{\sc Consulting}
% 
% I have provided a wide variety of statistical, policy, and statistical computing 
% consulting services to public and private sector clients at the national, state, 
% and local levels of government. 

% \section{\sc Grant Awards}

% (ED-GRANTS-031215-002)
% Wisconsin Department of Public Instruction. 2015. Bringing Evidence Based 
% Practices to Practitioners in Wisconsin. A proposal to the Institute of Education 
% Sciences Statewide Longitudinal Data System Data Use Competition.  
% [funded \$5.25 million over 4 years, project director]
% 
% % (HHS-2012-ACF-ACYF-CO-0270)
% Wisconsin Department of Children and Families. 2012. Improving Outcomes for Children in Out of Home Care through Coordination. A proposal to the Administration of Children, Youth and Families 
%  Child Welfare-Education System Collaboration to Increase Educational Stability Competition. [funded \$500,000 over 2 years]
% 
% Knowles, Jared. 2013. Dissertation Development Grant for Compilation of School Board Election Records Database. University of Wisconsin - Madison Summer Initiative Funds. [funded]
% 
% Knowles, Jared. 2012. Dissertation Development Grant for Collection of School Board Election Records. University of Wisconsin - Madison Summer Initiative Funds. [funded]
% 
% \section{\sc Skills} 
% \begin{list2}
% \item Statistical Packages:  R, Stan, SPSS, and Stata
% \item Languages:  R, Python, SQL, \LaTeX
% \item R Packages: Creator \textbf{merTools}, \textbf{eeptools}, deep experience with caret, ggplot2, data.table, knitr, lme4, and more
% \item Operating Systems:  Ubuntu, Ubuntu Server, SUSE Server, Windows
% \item For more information visit GitHub: \url{http://www.github.com/jknowles}\\
% \end{list2}

% \section{\sc Statistical Training}
% \begin{list2}
% \item Multivariate regression
% \item Mixed effect modeling, including hierarchical linear modeling
% \item Applied predictive modeling and machine learning
% \item Unsupervised learning and cluster analysis
% \item Generalized linear modeling
% \item Structural equation modeling
% \item Bayesian analysis
% \end{list2}

% \vspace{-2mm}
% \section{\sc Languages}
% 
% \begin{list2}
% \item English--native
% \item German--familiar
% \end{list2}


\end{resume}
\end{document}
