\documentclass[margin,line]{res}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[normalem]{ulem}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jared E. Knowles \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2.75in}}
Civilytics Consulting LLC & {\it Voice:}  (617) 393-0263 \\            
28 Rangeley Road & {\it www:} \url{www.civilytics.com} \\           
Watertown, MA 02472 & {\it E-mail:}  jared@civilytics.com\\       
 & {\it Twitter:} @jknowles      \\   
\end{tabular}

\section{\sc Research Interests}
Democratic accountability, government performance analytics, applied statistical 
modeling, politics of evidence, criminal justice, education policy, public finance and budgets

\section{\sc Education}
{\bf University of Wisconsin -- Madison}, Madison, Wisconsin USA\\
%{\em Department of Political Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Political Science, May, 2015
\begin{list2}
\vspace*{.05in}
%\item Subfields: American politics, political methodology
\item Dissertation Title: \emph {School Boards and the Democratic Promise} 
%\item Advisor:  John Witte
\end{list2}
\vspace*{.05in}
\item[] M.A., Political Science,  May 2009
\end{list1}

{\bf Pacific University}, Forest Grove, Oregon USA\\
%{\em Department of Politics and Government} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Politics and Government,  May, 2008
\item[] B.A., German Studies, May, 2008
\end{list1}


\section{\sc Honors and Awards} 

\href{https://www.lafollette.wisc.edu/news/2015-gladfelter-winners-announced}{Lloyd D. Gladfelter Award for Government Innovation} from the La Follette School of Public Affairs at UW-Madison, 2015

\vspace*{-2.5mm}

Institute for Education Sciences Predoctoral Fellowship, Interdisciplinary Training Program (ITP) at Wisconsin Center for Education Research, 2009-2015

\vspace*{-2.5mm}
German Academic Exchange Service (DAAD) Undergraduate Fellow, 2006-2007

\section{\sc Work \\ Experience}
{\bf Civilytics Consulting LLC}, Watertown, Massachusetts USA
\vspace{-.3cm}

{\em President} \hfill {\bf August 2016 - Present}\\
Provide statistical analysis, policy recommendations, and training to government, 
journalists, non-profits, and the general public. 
\begin{list2}
\item Develop public reports and database on police funding, arrest behavior, and the campus 
policing sector to inform the public and policymakers using available data.
\item Develop analytic software to inform strategic planning for K-12 and higher 
education policymakers. 
\item Train hundreds of education data analysts in statistical methods, programming, 
and policy evaluation.
\item Train community organizations, journalists, and city officials on budget 
analysis with an emphasis on policing and corrections budgets. 
\end{list2}


\vspace{-.1cm}

{\bf Department of Public Instruction}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Senior Research Analyst} \hfill {\bf January 2013 - June 2016}\\
Supported advancement of the State Superintendent's agenda by producing quantitative 
analyses tailored for stakeholders, policymakers, and educators. Supported state agency budget development. \\

\vspace*{-.3cm}

{\em Policy Research Advisor} \hfill {\bf January 2011 - January 2013} \\
Conducted policy research using administrative records on a tight timeline to 
support key decisions by senior agency leadership including budget development. \\

\vspace{-.3cm}
{\em Policy Analysis Intern} \hfill {\bf September 2010 - January 2011}\\
Provided statistical programming support to the Office of Education Accountability.

{\bf Office of the Governor}, Madison, Wisconsin USA

\vspace{-.3cm}
{\em Policy Assistant for Race to the Top Application} \hfill {\bf September 2009 - May 2010}\\
Assisted in preparing Wisconsin's Race to the Top federal education funding 
application. 

% \begin{list2}
% \item Worked with the state education agency staff to develop achievement targets grounded in data.
% \item Presented data visualization of comparative education data to senior policymakers.
% \end{list2}

\section{\sc Select Publications}
Knowles, Jared. E. (2020). ``How to Take Back the Budget.'' \emph{Community Resource 
Hub for Safety \& Accountability.} \href{https://communityresourcehub.org/resources/how-to-take-back-the-budget/}{Available online.}

Knowles, Jared. E. (2020). ``Policing the American University.'' \emph{Civilytics 
Data Report} \#1. \href{https://www.civilytics.com/publication/cpd-report/}{Available online.}

Geller, Wendy, Dorothyjean Cratty, and Jared Knowles. (2019). \uline{Education Data Done Right: Lessons from the Trenches of Applied Data Science.} \emph{LeanPub.} 
\href{https://www.eddatadoneright.com}{Available online.}

Knowles, Jared E. (2020). ``Integrating Publicly Available External Data With an SLDS: Building 
Policy Relevance and Capacity.'' \emph{College & Career Readiness & Success Center.} 
SLDS Issue Brief. [Forthcoming, 2020]

Knowles, Jared E. and Carl Frederick. (2018). merTools: Tools for Analyzing Mixed 
Effect Regression Models. R package version 0.4.1. 
\url{https://CRAN.R-project.org/package=merTools}

Knowles, Jared E. and William Clune. (2016). ``Delivery of State-provided Predictive
Analytics to Schools: Wisconsin’s DEWS and the Proposed EWIMS Dashboard.'' 
\emph{WCER Working Paper.} No. 2016-3, July 2016. \href{http://wcer-web.ad.education.wisc.edu/docs/working-papers/Working_Paper_No_2016_03.pdf}{Available online.}

Knowles, Jared E. and Deven Carlson. (2016). ``The Effect of English Proficiency Classification 
on Future Outcomes: Evidence from a Statewide Discontinuity.'' \emph{Journal of Policy Analysis 
and Management.} 35:3, 559-586. 

Knowles, Jared E. (2015). ``School Boards and the Democratic Promise,'' (PhD diss., University of 
Wisconsin - Madison, 2015).

Knowles, Jared E. (2015). ``Of Needles and Haystacks: Building an Accurate Statewide 
Dropout Early Warning System in Wisconsin.'' \emph{Journal of Educational Data 
Mining.} 7:3, 18-67. 
\href{http://www.educationaldatamining.org/JEDM/index.php/JEDM/article/view/JEDM082}{Available online.}

\vspace*{3mm}

\section{\sc Professional Activities and Service}
% 
\begin{list2}
\item Urban Institute Education Data Portal Advisory Board member, 2020-2021
\item Institute for Education Sciences Peer Review Panel Member, 2019
\item Faculty Advisor, Strategic Data Project, Center for Education Policy Research (CEPR) at Harvard University, 2012 -- present
\item National Forum on Education Statistics at the Institute for Education Sciences, \emph{state agency representative for Wisconsin}, 2011 -- 2016
\item Wisconsin Department of Public Instruction R User Group \emph{founder, organizer}, 
2012 -- 2016 
\item Data Analysis Technical Assistance-Community of Practice in Education 
(DATA-COPE) \emph{founder, organizer}, 2014 -- 2018
\item State Superintendent's Wisconsin Education Research Advisory Council (WERAC), 
\emph{chair, organizer}, 2012 -- 2016
\end{list2}

\vspace{-2mm}

\section{\sc Statistical Training}
\begin{list2}
\item Mixed effect modeling, including hierarchical linear and structural equation modeling
\item Applied predictive modeling, machine learning, deep learning with Keras
\item Unsupervised learning and cluster analysis
\item Bayesian analyses
\item For more details visit GitHub: \url{https://www.github.com/jknowles}\\
\end{list2}

\vspace{-2mm}

% \section{\sc Languages}
% 
% \begin{list2}
% \item English--native
% \item German--familiar
% \end{list2}


\end{resume}
\end{document}


